---
title: "Data Science Lab Project"
author: "Pasquale Gravante"
date: "`r format(Sys.Date(), '%B %d, %Y')`" # Displays today's date in the format "Month Day, Year"
format: 
  html:
    warning: false
    messages: false
    code-fold: false
    code-summary: "Show the code"
    keep-md: true # Keeps the markdown file generated in the conversion process
    toc: true # Includes a table of contents
    toc-depth: 2 # Depth of the table of contents
    toc-title: "Contents" # Title of the table of contents
---

# INTRODUCTION

## Dataset description

The dataset used in this project, provided by Banca d'Italia, is a comprehensive survey on financial literacy among Italian adults. The survey, part of an OECD initiative, aims to create an internationally comparable dataset to evaluate financial literacy and inclusion. It includes approximately 2,500 respondents who were interviewed using two different methods: face-to-face interviews and tablet-based responses. The dataset contains detailed socio-demographic information, financial knowledge scores, behavioral data on financial practices, and attitudes towards financial management. Key variables include gender, age, educational qualification, employment status, geographic location, and various aspects of financial behavior and attitudes.

## Idea and motivations

Financial literacy is a critical factor for individual and household economic well-being. Despite the importance of financial knowledge, many individuals struggle with understanding basic financial concepts, which can lead to poor financial decisions and increased financial vulnerability.

The motivation behind this project is to analyze the current state of financial literacy in Italy, identify key factors influencing it, and develop targeted strategies to improve financial education. By leveraging this rich dataset, we can gain insights into the financial behaviors and attitudes of different demographic groups and understand how financial literacy impacts their financial decision-making.

## Aim of the project

The primary aim of this project is to assess and improve financial literacy among Italian adults by conducting an analysis of the provided dataset. Specifically, the project has the following objectives:

**Assess the Current Level of Financial Literacy**: Evaluate the financial literacy scores across various demographic groups to understand the disparities and identify areas needing improvement.

**Identify Key Influencing Factors**: Determine the socio-demographic and economic factors that significantly impact financial literacy and financial behaviors.

**Examine Financial Resilience**: Analyze how different levels of financial literacy affect the ability of individuals to manage financial shocks and unexpected expenses.

**Explore Financial Decision-Making**: Investigate the relationship between financial literacy and the quality of financial decisions, such as investment choices and debt management.

**Investigate Regional Disparities:** Assess regional differences in financial literacy and access to financial education resources to identify areas where interventions are most needed.

# DATA PRE-PROCESSING

In this section the necessary data and libraries are imported:

```{r}
library(effects)
library(broom)
library(MASS)
library(randomForest)
library(cluster)
library(factoextra)
library(NbClust)
library(arules)
library(arulesViz)
library(dplyr)
library(tidyr)
library(caret)
library(ggplot2)
library(readr)
library(forcats)
library(knitr)
library(MASS)
```

```{r}
df <- read.csv("Dati Ricerca BI.csv")
```

## Cleaning

```{r}
df <- df[,-c(104,105)]
df <- df %>% mutate(across(starts_with("Q"), as.factor))
df$AREA5 <- as.factor(df$AREA5)
df <- df %>%
  mutate(across(starts_with("q"), ~ fct_recode(., NULL = "-99", NULL = "_99")))
df$qd7 <- as.numeric(df$qd7)
```

## Data Manipulation

Creation of an age group variable:

```{r}
df <- df %>%
  mutate(age = case_when(
    qd7 < 18 ~ 'under_18',
    qd7 >= 18 & qd7 < 30 ~ '18_29',
    qd7 >= 30 & qd7 < 45 ~ '30_44',
    qd7 >= 45 & qd7 < 60 ~ '45_59',
    qd7 >= 60 ~ '60+'
  ))
df <- df %>%
  mutate(age = as.factor(age))
```

Grouping regions:

```{r}
df <- df %>%
  mutate(region = case_when(
    AREA5 %in% c(1, 2) ~ 'North',
    AREA5 == 3 ~ 'Centre',
    AREA5 %in% c(4, 5) ~ 'South & Islands'
  )) %>% mutate(region = as.factor(region))
```

Sex variable:

```{r}
df <- df %>%
  mutate(sex = case_when(
    qd1 == 0 ~ 'Female',
    qd1 == 1 ~ 'Male')) %>% mutate(sex = as.factor(sex))
```

Education variable:

```{r}
df <- df %>%
  mutate(education = case_when(
    qd9 %in% c('6', '7') ~ 'No education',
    qd9 %in% c('5', '4') ~ 'Primary education',
    qd9 == '3' ~ 'Secondary education',
    qd9 == '1' ~ 'University'
  )) %>%
  mutate(education = factor(education, levels = c('No education', 'Primary education', 'Secondary education', 'University'), ordered = TRUE))
```

Employment variable:

```{r}
df <- df %>%
  mutate(employment = case_when(
    qd10 %in% c(1, 2) ~ 'Employed',
    qd10 %in% c(4, 5) ~ 'Not in labor force',
    qd10 == 6 ~ 'Retired',
    qd10 == 9 ~ 'Student'
  )) %>%
  mutate(employment = factor(employment, levels = c('Employed', 'Not in labor force', 'Retired', 'Student')))
```

## Feature engineering

### Interaction variables

```{r}
df <- df %>%
  mutate(inter_education_employment = interaction(education, employment)) %>%
  mutate(inter_sex_employment = interaction(sex, employment)) %>%
  mutate(inter_sex_education = interaction(sex, education)) %>%
  mutate(inter_region_education = interaction(region, education)) %>%
  mutate(inter_age_education = interaction(age, education)) %>%
  mutate(inter_age_region = interaction(age, region)) 

```

### Financial behavior score

```{r}
# Rule 1: 1 point if personally or jointly responsible for money management AND actively keeping track of money

rule_1 <- as.numeric((df$qf1 %in% c(1, 2) & df$qf2 == 1))

# Rule 2: 1 point for any type of active saving (QF3_1 - QF3_99)

df <- df %>%
  mutate(across(starts_with("qf3_"), ~ as.numeric(as.character(.))))

active_saving_qf3 <- ifelse(rowSums(df[, grep("^qf3_", names(df))], na.rm = TRUE) >= 1 & df$qf3_8 != 1 & df$qf3_99 != 1, 1, 0)

rule_2 <- as.numeric(active_saving_qf3 == 1)

# Rule 3: 1 point if no borrowing to make ends meet

rule_3 <- with(df, ifelse(qf11 == 0, 1, 
                                   ifelse(qf11 == 1 & !(qf12_3_e == 1 | qf12_3_f == 1 | qf12_3_g == 1 | 
                                                         qf12_4_k == 1 | qf12_4_l == 1 | qf12_5_m == 1 | 
                                                         qf12_5_o == 1 | qf12_6_p == 1 | qf12_6_q == 1 | qf12_99 == 1 | qf12_97 == 1),1,0)))

# Rule 4: Choosing products

qp_d1 <- as.numeric(df$qprod2 %in% c(1, 4))
qp_d2 <- rep(0, nrow(df))
rows_to_check <- df$qprod2 %in% c(1, 4)

### Check variables for value 1 in the first set (answers that give 2 points)

df <- df %>%
  mutate(across(c("qprod3_2", "qprod3_3", "qprod3_4", "qprod3_5", "qprod3_6", "qprod3_7", "qprod3_8", "qprod3_10"), ~ as.numeric(as.character(.))))

qp_d2[rows_to_check] <- ifelse(
  rowSums(df[rows_to_check, c("qprod3_2", "qprod3_3", "qprod3_4", "qprod3_5", "qprod3_6", "qprod3_7", "qprod3_8", "qprod3_10")], na.rm = TRUE) > 0,
  2,
  0
)

### Check variables for value 1 in the second set (answers that give 1 point)

df <- df %>%
  mutate(across(c("qprod3_1", "qprod3_9", "qprod3_11", "qprod3_12", "qprod3_13", "qprod3_14", "qprod3_15", "qprod3_16", "qprod3_17", "qprod3_18"), ~ as.numeric(as.character(.))))

qp_d2[rows_to_check & qp_d2 == 0] <- ifelse(
  rowSums(df[rows_to_check & qp_d2 == 0, c("qprod3_1", "qprod3_9", "qprod3_11", "qprod3_12", "qprod3_13", "qprod3_14", "qprod3_15", "qprod3_16", "qprod3_17", "qprod3_18")], na.rm = TRUE) > 0,
  1,
  0
)

## Create the rule_4 variable and assign values based on intermediate variables scores

rule_4 <- ifelse(qp_d2 == 2, 2, ifelse(qp_d1 == 1 | qp_d2 == 1, 1, 0))

# Creating Rule 5

rule_5 <- ifelse(df$qf10_6 %in% c(1, 2) & df$qf10_7 %in% c(1, 2), 2,
                             ifelse(df$qf10_6 %in% c(1, 2) | df$qf10_7 %in% c(1, 2), 1, 0))

# Creating Rule 6 - Financial behaviours

rule_6 <- ifelse(df$qf10_1 %in% c(1, 2) & df$qf10_4 %in% c(1, 2), 2,
                             ifelse(df$qf10_1 %in% c(1, 2) | df$qf10_4 %in% c(1, 2), 1, 0))

# Summing up rules to get the financial behaviour score (goes from 0 to 9)

df$fin_behaviour_score = rowSums(cbind(rule_1, rule_2, rule_3, rule_4, rule_5, rule_6), na.rm = TRUE)
```

### Financial knowledge score

```{r}
rule_7 <- as.numeric(df$qk3 == 3)
rule_8 <- as.numeric(df$qk4 == 0)
rule_9 <- as.numeric(df$qk5 == 102)
rule_10 <- as.numeric(df$qk5 == 102 & df$qk6 == 1)
rule_11 <- as.numeric(df$qk7_1 == 1)
rule_12 <- as.numeric(df$qk7_2 == 1)
rule_13 <- as.numeric(df$qk7_3 == 1)

### Summing up the rules to create the score

df$fin_knowledge_score = rowSums(cbind(rule_7, rule_8, rule_9, rule_10, rule_11, rule_12, rule_13), na.rm = TRUE)
```

### Financial attitude score

```{r}
# Specify the columns to be recoded
columns_to_recode <- c("qf10_1", "qf10_2", "qf10_3", "qf10_4", "qf10_5", "qf10_6", "qf10_7", "qf10_8", "qf10_9", "qf10_10", "qf10_11", "qf10_12")

df <- df %>%
  mutate(across(all_of(columns_to_recode), as.factor))

df <- df %>%
  mutate(across(all_of(columns_to_recode), ~ fct_na_value_to_level(fct_recode(., `3` = "-97"), level = "3")))

### Creating the rule

# Specify the columns for rescaling
columns_to_rescale <- c("qf10_2", "qf10_8")

# Create a temporary data frame for rescaled values
temp_data <- df[columns_to_rescale]
temp_data$qf10_2 <- as.numeric(temp_data$qf10_2)
temp_data$qf10_8 <- as.numeric(temp_data$qf10_8)

# Rescale values from 1 to 5 to 0 to 4 in the temporary data frame
temp_data <- temp_data - 1

# Calculate the average and store it in rule_14
temp_data$rule_14temp <- rowMeans(temp_data, na.rm = TRUE)
rule_14 = temp_data$rule_14temp
df$fin_attitude_score = rule_14
```

### Financial literacy score

```{r}
df$fin_literacy_score <- rowSums(df[, c("fin_behaviour_score", "fin_attitude_score", "fin_knowledge_score")], na.rm = TRUE)
```

Creating categories:

```{r}
# Create categories for the fin_literacy_score
df <- df %>%
  mutate(fin_lit_category = case_when(
    fin_literacy_score < 4 ~ "Low",
    fin_literacy_score < 8 ~ "Very Low",
    fin_literacy_score < 12 ~ "Average",
    fin_literacy_score < 16 ~ "High",
    fin_literacy_score >= 16 ~ "Very High"
  ))

# Convert to factor with ordered levels
df$fin_lit_category <- factor(df$fin_lit_category, 
                                    levels = c("Very Low", "Low", "Average", "High", "Very High"), ordered = TRUE)
```

# EDA

## Tables

In this section the dataset is going to be explored:

```{r}
df <- df %>% filter(!is.na(education), !is.na(employment))
```

```{r}
# Summary table for age_group
age_summary <- df %>%
  group_by(age) %>%
  summarise(Count = n()) %>%
  kable(col.names = c("Age", "Count"), caption = "Distribution of Age Groups")

# Summary table for education
education_summary <- df %>%
  group_by(education) %>%
  summarise(Count = n()) %>%
  kable(col.names = c("Education Level", "Count"), caption = "Distribution of Education Levels")

# Summary table for region
region_summary <- df %>%
  group_by(region) %>%
  summarise(Count = n()) %>%
  kable(col.names = c("Region", "Count"), caption = "Distribution of Regions")

# Summary table for employment_status
employment_status_summary <- df %>%
  group_by(employment) %>%
  summarise(Count = n()) %>%
  kable(col.names = c("Employment Status", "Count"), caption = "Distribution of Employment Status")

sex_summary <- df %>%
  group_by(sex) %>%
  summarise(Count = n()) %>%
  kable(col.names = c("Gender", "Count"), caption = "Distribution of Genders")

# Display the tables
print(age_summary)
print(education_summary)
print(region_summary)
print(employment_status_summary)
print(sex_summary)

```

## 

## Visualizations

```{r}
ggplot(df, aes(x = fin_lit_category)) +
  geom_bar(fill = "steelblue") +
  labs(title = "Distribution of Financial Literacy Categories", x = "Financial Literacy Category", y = "Count") +
  theme_minimal()
```

```{r}
ggplot(df, aes(x = age, y = fin_literacy_score)) +
  geom_boxplot(fill = "lightcoral") +
  labs(title = "Financial Literacy Scores by Age Group", x = "Age Group", y = "Financial Literacy Score")
```

```{r}
ggplot(df, aes(x = education, y = fin_literacy_score)) +
  geom_boxplot(fill = "lightblue") +
  labs(title = "Financial Literacy Scores by Education Level", x = "Education Level", y = "Financial Literacy Score")
```

```{r}
ggplot(df, aes(x = employment, y = fin_literacy_score)) +
  geom_boxplot(fill = "lightgreen") +
  labs(title = "Financial Literacy Scores by Employment", x = "Employment", y = "Financial Literacy Score")
```

```{r}
ggplot(df, aes(x = sex, y = fin_literacy_score)) +
  geom_boxplot(fill = "orange") +
  labs(title = "Financial Literacy Scores by Sex", x = "Sex", y = "Financial Literacy Score")
```

```{r}
ggplot(df, aes(x = region, y = fin_literacy_score)) +
  geom_boxplot(fill = "steelblue") +
  labs(title = "Financial Literacy Scores by Region", x = "Region", y = "Financial Literacy Score")
```

# MODELING

## Research question 1

Understanding the determinants of financial literacy through ordinal regression can inform policymakers and educators about:

-   Targeted educational programs for specific demographic groups.

-   Effective policy measures to improve financial literacy across different population segments.

-   Allocation of resources in areas where interventions are most needed.

### Ordinal regression

```{r}
# Fit the ordinal regression model
ord_model <- polr(fin_lit_category ~ age + education + region + employment + sex, data = df, Hess = TRUE)

# Summary of the model
summary(ord_model)
```

```{r}
# Calculate p-values for the model coefficients
coeftest <- coef(summary(ord_model))
p_values <- pnorm(abs(coeftest[, "t value"]), lower.tail = FALSE) * 2

# Combine coefficients and p-values into a data frame
ord_model_results <- cbind(coeftest, "p value" = p_values)

# Display the results
print(ord_model_results)
```

#### **Interpretation**

### Linear regression

#### Regional disparities model

```{r}
lm1 = lm(fin_literacy_score ~ region * education + 
                        region * employment +
                        age + sex, data = df)
summary(lm1)
```

None of the interaction terms between region and education or region and employment are statistically significant. This suggests that:

-   The effect of education on financial literacy does not significantly differ across regions.

-   The impact of employment status on financial literacy is relatively consistent across regions.

#### Gender and Socioeconomic Interaction Model

```{r}
lm2 = lm(fin_literacy_score ~ sex * education + 
                        sex * employment + 
                        sex * age +
                        region, data = df)
summary(lm2)
```

### Interpretation of Interactions

-   Sex and Education:

    -   The positive interaction between male and education.L (2.36899) suggests that the positive effect of education on financial literacy is stronger for males than for females.

-   Sex and Employment:

    -   The negative interaction between male and "Not in labor force" (-0.87067) indicates that being out of the labor force has a more negative impact on financial literacy for males than for females.

### Implications

-   Gender Differences: The impact of both education and employment status on financial literacy appears to differ significantly between males and females. This suggests that gender-specific approaches to financial education might be beneficial.

-   Education: Education remains a strong predictor of financial literacy, but its effect is more pronounced for males. This could indicate a need for targeted efforts to enhance the impact of education on financial literacy for females.

## Research question 2

What are the underlying patterns and relationships between various financial behaviors and attitudes among individuals, and how can these patterns help in designing targeted financial education programs?

### Feature selection

```{r}
# Seleziona tutte le variabili potenzialmente rilevanti
potential_features <- df %>%
  dplyr::select(
    fin_lit_category,
    starts_with("qf3"),
    qf4, qf8, qf13, qk1,
    education, employment, age, sex, # variabili demografiche
    qf10_1:qf10_12, # attitudini finanziarie dettagliate
    qk3:qk7_3, # domande specifiche sulla conoscenza finanziaria
  )

# Converti le variabili numeriche in fattori
potential_features <- potential_features %>%
  mutate(across(where(is.numeric), as.factor))

# Rimuovi le righe con valori mancanti
potential_features <- na.omit(potential_features)

# 2. Esegui Random Forest per l'importanza delle feature
set.seed(123)
rf_model <- randomForest(fin_lit_category ~ ., data = potential_features, importance = TRUE)

# 3. Calcola e stampa l'importanza delle feature
feature_importance <- importance(rf_model)
print(feature_importance)

# 4. Seleziona le top N feature più importanti
top_n_features <- 15
important_features <- row.names(feature_importance)[order(feature_importance[, "MeanDecreaseGini"], decreasing = TRUE)[1:top_n_features]]

final_selected_data <- potential_features %>%
  dplyr::select(all_of(important_features))
```

### Association rules

```{r}
# Converti i dati in transazioni
transactions <- as(final_selected_data, "transactions")

# Esegui l'algoritmo apriori con parametri più restrittivi
rules <- apriori(transactions, 
                 parameter = list(support = 0.1, confidence = 0.8, minlen = 2, maxlen = 10))

# Ordina le regole per lift
rules_sorted <- sort(rules, by = "lift", decreasing = TRUE)

# Funzione per ottenere regole diverse
get_diverse_rules <- function(rules, n = 3) {
  diverse_rules <- list()
  seen_rhs <- c()
  
  for (i in 1:length(rules)) {
    rule <- rules[i]
    rhs <- labels(rhs(rule))
    
    if (!(rhs %in% seen_rhs)) {
      diverse_rules <- c(diverse_rules, rule)
      seen_rhs <- c(seen_rhs, rhs)
    }
    
    if (length(diverse_rules) == n) break
  }
  
  return(diverse_rules)
}

# Ottieni le prime 3 regole diverse
diverse_rules <- get_diverse_rules(rules_sorted, 3)
diverse_rules <- diverse_rules[-1]

# Funzione per interpretare una regola
interpret_rule <- function(rule) {
  lhs <- labels(lhs(rule))
  rhs <- labels(rhs(rule))
  
  cat("Se un individuo:", "\n")
  for(item in lhs) {
    cat("- ", item, "\n")
  }
  cat("Allora è probabile che anche:", "\n")
  cat("- ", rhs, "\n")
  cat("Con una confidenza di", round(quality(rule)$confidence, 2), 
      "e un lift di", round(quality(rule)$lift, 2), "\n\n")
}

# Interpreta le prime 3 regole diverse
cat("Le prime 3 regole di associazione diverse:\n\n")
for(rule in diverse_rules) {
  interpret_rule(rule)
}
```

#### Interpretazione

## 

## Research question 3

### Data preparation

```{r}
df_2022 <- read.csv("Database_ENG.csv")
```

```{r}
calculate_digital_financial_literacy_score <- function(data) {
  # Knowledge component (qk7_4, qk7_5, qk7_6)
  knowledge_score <- with(data, 
    (qk7_4 == 0) + (qk7_5 == 1) + (qk7_6 == 0)
  )
  
  # Behaviour component (qs2_6, qs2_7, qs2_8, qs3_13)
  behaviour_score <- with(data,
    (qs2_6 %in% c(4, 5)) + 
    (qs2_7 %in% c(1, 2)) + 
    (qs2_8 %in% c(4, 5)) + 
    (qs3_13 %in% c(1, 2))
  )
  
  # Attitude component (qs4_1, qs4_2, qs4_3)
  attitude_score <- with(data,
    (qs4_1 %in% c(4, 5)) + 
    (qs4_2 %in% c(1, 2)) + 
    (qs4_3 %in% c(4, 5))
  )
  
  # Calculate raw score (0-10)
  raw_score <- knowledge_score + behaviour_score + attitude_score
  
  # Scale the score to 0-100
  scaled_score <- raw_score * 10
  
  return(scaled_score)
}

# Usage:
df_2022$digital_literacy_score <- calculate_digital_financial_literacy_score(df_2022)
```

```{r}
# Recode variables
df_2022 <- df_2022 %>%
  mutate(
    # Recode income
    income = case_when(
      qd13 == 1 ~ "Low",
      qd13 == 2 ~ "Medium",
      qd13 == 3 ~ "High",
      TRUE ~ NA_character_
    ),
    income = factor(income, levels = c("Low", "Medium", "High"), ordered = TRUE),
    
    # Recode gender
    gender = case_when(
      qd1 == 1 ~ "Male",
      qd1 == 0 ~ "Female",
      TRUE ~ NA_character_
    ),
    gender = factor(gender),
    
    # Recode age
    age = ifelse(qd7 == -99, NA, qd7),
    
    # Recode region into North, Centre, South & Islands
    region = case_when(
      qd2 %in% c(1, 2) ~ "North",
      qd2 == 3 ~ "Centre",
      qd2 %in% c(4, 5) ~ "South & Islands",
      TRUE ~ NA_character_
    ),
    region = factor(region),
    
    # Recode education
    education = case_when(
      qd9 %in% c(1, 2) ~ "University",
      qd9 %in% c(3, 4, 5) ~ "High school",
      qd9 %in% c(6, 7, 8) ~ "Middle school",
      qd9 %in% c(9, 10) ~ "Primary or less",
      TRUE ~ NA_character_
    ),
    education = factor(education, levels = c("Primary or less", "Middle school", "High school", "University"), ordered = TRUE),
    
    # Recode work situation
    work_situation = case_when(
      qd10 %in% c(1, 2, 3) ~ "Employed",
      qd10 %in% c(4, 5, 7, 8) ~ "Not in labor force",
      qd10 == 6 ~ "Retired",
      qd10 == 9 ~ "Student",
      qd10 == 10 ~ "Other",
      TRUE ~ NA_character_
    ),
    work_situation = factor(work_situation)
  ) %>%
  # Remove rows with NA in key variables
  filter(!is.na(income), !is.na(gender), !is.na(age), !is.na(region), !is.na(education), !is.na(work_situation))
```

### Multiple linear regression

```{r}
# Multiple linear regression
mlr_df <- lm(digital_literacy_score ~ age + education + income + gender + region + work_situation, data = df_2022)

# Summary of the model
summary(mlr_df)

# Tidy summary for easier interpretation
tidy_model <- tidy(mlr_df)
```

```{r}
# Visualize coefficients
ggplot(tidy_model, aes(x = reorder(term, estimate), y = estimate)) +
  geom_col() +
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate + std.error), width = 0.2) +
  coord_flip() +
  labs(title = "Demographic Factors Influencing Digital Financial Literacy",
       x = "Factors", y = "Estimated Effect on Digital Financial Literacy Score")
```

### ANOVA

```{r}
# ANOVA for categorical variables
anova_results <- list(
  income = aov(digital_literacy_score ~ income, data = df_2022),
  education = aov(digital_literacy_score ~ education, data = df_2022),
  region = aov(digital_literacy_score ~ region, data = df_2022),
  work_situation = aov(digital_literacy_score ~ work_situation, data = df_2022)
)

# Print ANOVA summaries
lapply(anova_results, summary)
```

### Ordinal logistic regression

```{r}
# Recode digital risk perception into ordinal categories
df_2022 <- df_2022 %>%
  mutate(
    digital_risk_perception = case_when(
      qs4_1 == 1 ~ "Very High",
      qs4_1 == 2 ~ "High",
      qs4_1 == 3 ~ "Medium",
      qs4_1 == 4 ~ "Low",
      qs4_1 == 5 ~ "Very Low",
      TRUE ~ NA_character_
    ),
    digital_risk_perception = factor(digital_risk_perception, 
                                     levels = c("Very Low", "Low", "Medium", "High", "Very High"),
                                     ordered = TRUE)
  )

# Fit the ordinal logistic regression model
model_risk <- polr(digital_risk_perception ~ digital_literacy_score + 
                   education + income + age + gender + region, 
                   data = df_2022, Hess = TRUE)

# Model summary
summary(model_risk)

# Tidy output of the model
tidy_model <- tidy(model_risk)
print(tidy_model)

# Calculate and print odds ratios with confidence intervals
odds_ratios <- exp(coef(model_risk))
ci <- exp(confint(model_risk))
odds_ratios_table <- cbind(OR = odds_ratios, ci)
print(odds_ratios_table)

# Optional: Create a formatted table of odds ratios
library(knitr)
kable(odds_ratios_table, digits = 3, caption = "Odds Ratios with 95% Confidence Intervals")
```

```{r}
# Create new data for predictions
new_data <- data.frame(
  digital_literacy_score = seq(
    min(df_2022$digital_literacy_score, na.rm = TRUE),
    max(df_2022$digital_literacy_score, na.rm = TRUE),
    length.out = 100
  ),
  education = "High school",  # Mode or reference level
  income = "Medium",          # Mode or reference level
  age = mean(df_2022$age, na.rm = TRUE),
  gender = "Female",          # Mode or reference level
  region = "North"            # Mode or reference level
)

# Predict probabilities
predicted_probs <- predict(model_risk, newdata = new_data, type = "probs")

# Prepare data for plotting
plot_data <- cbind(new_data, predicted_probs)
plot_data_long <- pivot_longer(plot_data, 
                               cols = c("Very Low", "Low", "Medium", "High", "Very High"),
                               names_to = "risk_level", 
                               values_to = "probability")

# Plot predicted probabilities
ggplot(plot_data_long, aes(x = digital_literacy_score, y = probability, color = risk_level)) +
  geom_line() +
  labs(title = "Predicted Probabilities of Digital Risk Perception",
       x = "Digital Literacy Score",
       y = "Probability",
       color = "Risk Level") +
  theme_minimal()

# Visualize the effect of digital literacy score on risk perception
plot(effect("digital_literacy_score", model_risk))
```
