---
title: "Data Science Lab Project"
author: "Pasquale Gravante & Antonio Mastroianni"
date: "2023-10-12"
output: pdf_document
---

# Loading libraries 

```{r}
library(dplyr)
```

# Loading data

```{r}
survey_data <- read.csv("~/Downloads/FINANCIAL LITERACY BANCA ITALIA/Dati Ricerca BI.csv")
```

# Data pre-processing

We create 3 different kind of scores and then we sum them up to obtain a unique financial literacy score.

## Financial behaviour score

```{r}

# Create the Financial literacy score

survey_data$financial_literacy_score <- 0

# Rule 1: 1 point if personally or jointly responsible for money management AND actively keeping track of money - Financial behaviours

rule_1 <- as.numeric((survey_data$qf1 %in% c(1, 2) & survey_data$qf2 == 1))

```

```{r}

# Rule 2: 1 point for any type of active saving (QF3_1 - QF3_99) - Financial behaviours

## Create a variable for active saving based on QF3_1 - QF3_99

active_saving_qf3 <- ifelse(rowSums(survey_data[, grep("^qf3_", names(survey_data))], na.rm = TRUE) >= 1 & survey_data$qf3_8 != 1 & survey_data$qf3_99 != 1, 1, 0)

## Creating the rule variable

rule_2 <- as.numeric(survey_data$active_saving_qf3 == 1)

```

```{r}

# Rule 3: 1 point if no borrowing to make ends meet - Financial behaviours

rule_3 <- with(survey_data, ifelse(qf11 == 0, 1, 
                                   ifelse(qf11 == 1 & !(qf12_3_e == 1 | qf12_3_f == 1 | qf12_3_g == 1 | 
                                                         qf12_4_k == 1 | qf12_4_l == 1 | qf12_5_m == 1 | 
                                                         qf12_5_o == 1 | qf12_6_p == 1 | qf12_6_q == 1 | qf12_99 == 1 | qf12_97 == 1),1,0)))

```

```{r}

# Rule 4: Financial behaviour - Choosing products

## Intermediate variable QP_D1

qp_d1 <- as.numeric(survey_data$qprod2 %in% c(1, 4))

## Create the intermediate variable qp_d2

qp_d2 <- rep(0, nrow(survey_data))

### Check rows where qprod2 is 1 or 4

rows_to_check <- survey_data$qprod2 %in% c(1, 4)

### Check variables for value 1 in the first set (answers that give 2 points)

qp_d2[rows_to_check] <- ifelse(
  rowSums(survey_data[rows_to_check, c("qprod3_2", "qprod3_3", "qprod3_4", "qprod3_5", "qprod3_6", "qprod3_7", "qprod3_8", "qprod3_10")], na.rm = TRUE) > 0,
  2,
  0
)

### Check variables for value 1 in the second set (answers that give 1 point)

qp_d2[rows_to_check & qp_d2 == 0] <- ifelse(
  rowSums(survey_data[rows_to_check & qp_d2 == 0, c("qprod3_1", "qprod3_9", "qprod3_11", "qprod3_12", "qprod3_13", "qprod3_14", "qprod3_15", "qprod3_16", "qprod3_17", "qprod3_18")], na.rm = TRUE) > 0,
  1,
  0
)

## Create the rule_4 variable and assign values based on intermediate variables scores

rule_4 <- ifelse(qp_d2 == 2, 2, ifelse(qp_d1 == 1 | qp_d2 == 1, 1, 0))

```

```{r}
# Creating Rule 5 - Financial behaviours

rule_5 <- ifelse(survey_data$qf10_6 %in% c(1, 2) & survey_data$qf10_7 %in% c(1, 2), 2,
                             ifelse(survey_data$qf10_6 %in% c(1, 2) | survey_data$qf10_7 %in% c(1, 2), 1, 0))
```

```{r}
# Creating Rule 6 - Financial behaviours

rule_6 <- ifelse(survey_data$qf10_1 %in% c(1, 2) & survey_data$qf10_4 %in% c(1, 2), 2,
                             ifelse(survey_data$qf10_1 %in% c(1, 2) | survey_data$qf10_4 %in% c(1, 2), 1, 0))
```

```{r}

# Summing up rules to get the financial behaviour score (goes from 0 to 9)

survey_data$financial_behaviour_score = rowSums(cbind(rule_1, rule_2, rule_3, rule_4, rule_5, rule_6))
```


## Financial Knowledge score

```{r}
rule_7 <- as.numeric(survey_data$qk3 == 3)
```

```{r}
rule_8 <- as.numeric(survey_data$qk4 == 0)
```

```{r}
rule_9 <- as.numeric(survey_data$qk5 == 102)
```

```{r}
rule_10 <- as.numeric(survey_data$qk5 == 102 & survey_data$qk6 == 1)
```

```{r}
rule_11 <- as.numeric(survey_data$qk7_1 == 1)
```

```{r}
rule_12 <- as.numeric(survey_data$qk7_2 == 1)
```

```{r}
rule_13 <- as.numeric(survey_data$qk7_3 == 1)
```

### Summing up the rules to create the score

```{r}
survey_data$financial_knowledge_score = rowSums(cbind(rule_7, rule_8, rule_9, rule_10, rule_11, rule_12, rule_13))
```

## Financial attitude score

### Recoding some variables 

```{r}
# Specify the columns to be recoded
columns_to_recode <- c("qf10_1", "qf10_2", "qf10_3", "qf10_4", "qf10_5", "qf10_6", "qf10_7", "qf10_8", "qf10_9", "qf10_10", "qf10_11", "qf10_12")

# Recode -97, -98, -99 as 3 in the specified columns
survey_data[columns_to_recode] <- lapply(survey_data[columns_to_recode], function(x) ifelse(x %in% c(-97, -98, -99), 3, x))
```

### Creating the rule

```{r}
# Specify the columns for rescaling
columns_to_rescale <- c("qf10_2", "qf10_8")

# Create a temporary data frame for rescaled values
temp_data <- survey_data

# Rescale values from 1 to 5 to 0 to 4 in the temporary data frame
temp_data[columns_to_rescale] <- temp_data[columns_to_rescale] - 1

# Calculate the average and store it in rule_14
temp_data$rule_14temp <- rowMeans(temp_data[columns_to_rescale], na.rm = TRUE)
rule_14 = temp_data$rule_14temp
```

### Adding the score to the Financial Attitude score to the dataset

```{r}
survey_data$financial_attitude_score = rule_14
```

## Getting the final **Financial literacy score**

```{r}

survey_data$financial_literacy_score <- rowSums(survey_data[, c("financial_behaviour_score", "financial_attitude_score", "financial_knowledge_score")], na.rm = TRUE)

```

