----
title: "Data Science Lab Project"
author: "Pasquale Gravante & Antonio Mastroianni & Angelo Giuseppe Limone & Pasquale Formicola"
date: "2023-10-12"
output: pdf_document
---

# Loading libraries 

```{r}
library(corrplot)
library(survey)
library(dplyr)
library(jtools)
library(factoextra)
library(ggplot2)
library(GGally)
library(cluster)
library(fpc)
library(reshape2)
library(caret)
library(MASS)
library(stats)
library(FactoMineR)
```

# Loading data

```{r}
survey_data <- read.csv("~/Downloads/FINANCIAL LITERACY BANCA ITALIA/Dati Ricerca BI.csv")
```

# Data pre-processing

We create 3 different kind of scores and then we sum them up to obtain a unique financial literacy score.

## Financial behaviour score

```{r}

# Create the Financial literacy score

survey_data$financial_literacy_score <- 0

# Rule 1: 1 point if personally or jointly responsible for money management AND actively keeping track of money - Financial behaviours

rule_1 <- as.numeric((survey_data$qf1 %in% c(1, 2) & survey_data$qf2 == 1))

```

```{r}

# Rule 2: 1 point for any type of active saving (QF3_1 - QF3_99) - Financial behaviours

## Create a variable for active saving based on QF3_1 - QF3_99

active_saving_qf3 <- ifelse(rowSums(survey_data[, grep("^qf3_", names(survey_data))], na.rm = TRUE) >= 1 & survey_data$qf3_8 != 1 & survey_data$qf3_99 != 1, 1, 0)

## Creating the rule variable

rule_2 <- as.numeric(active_saving_qf3 == 1)

```

```{r}

# Rule 3: 1 point if no borrowing to make ends meet - Financial behaviours

rule_3 <- with(survey_data, ifelse(qf11 == 0, 1, 
                                   ifelse(qf11 == 1 & !(qf12_3_e == 1 | qf12_3_f == 1 | qf12_3_g == 1 | 
                                                         qf12_4_k == 1 | qf12_4_l == 1 | qf12_5_m == 1 | 
                                                         qf12_5_o == 1 | qf12_6_p == 1 | qf12_6_q == 1 | qf12_99 == 1 | qf12_97 == 1),1,0)))

```

```{r}

# Rule 4: Financial behaviour - Choosing products

## Intermediate variable QP_D1

qp_d1 <- as.numeric(survey_data$qprod2 %in% c(1, 4))

## Create the intermediate variable qp_d2

qp_d2 <- rep(0, nrow(survey_data))

### Check rows where qprod2 is 1 or 4

rows_to_check <- survey_data$qprod2 %in% c(1, 4)

### Check variables for value 1 in the first set (answers that give 2 points)

qp_d2[rows_to_check] <- ifelse(
  rowSums(survey_data[rows_to_check, c("qprod3_2", "qprod3_3", "qprod3_4", "qprod3_5", "qprod3_6", "qprod3_7", "qprod3_8", "qprod3_10")], na.rm = TRUE) > 0,
  2,
  0
)

### Check variables for value 1 in the second set (answers that give 1 point)

qp_d2[rows_to_check & qp_d2 == 0] <- ifelse(
  rowSums(survey_data[rows_to_check & qp_d2 == 0, c("qprod3_1", "qprod3_9", "qprod3_11", "qprod3_12", "qprod3_13", "qprod3_14", "qprod3_15", "qprod3_16", "qprod3_17", "qprod3_18")], na.rm = TRUE) > 0,
  1,
  0
)

## Create the rule_4 variable and assign values based on intermediate variables scores

rule_4 <- ifelse(qp_d2 == 2, 2, ifelse(qp_d1 == 1 | qp_d2 == 1, 1, 0))

```

```{r}
# Creating Rule 5 - Financial behaviours

rule_5 <- ifelse(survey_data$qf10_6 %in% c(1, 2) & survey_data$qf10_7 %in% c(1, 2), 2,
                             ifelse(survey_data$qf10_6 %in% c(1, 2) | survey_data$qf10_7 %in% c(1, 2), 1, 0))
```

```{r}
# Creating Rule 6 - Financial behaviours

rule_6 <- ifelse(survey_data$qf10_1 %in% c(1, 2) & survey_data$qf10_4 %in% c(1, 2), 2,
                             ifelse(survey_data$qf10_1 %in% c(1, 2) | survey_data$qf10_4 %in% c(1, 2), 1, 0))
```

```{r}

# Summing up rules to get the financial behaviour score (goes from 0 to 9)

survey_data$financial_behaviour_score = rowSums(cbind(rule_1, rule_2, rule_3, rule_4, rule_5, rule_6))
```


## Financial Knowledge score

```{r}
rule_7 <- as.numeric(survey_data$qk3 == 3)
```

```{r}
rule_8 <- as.numeric(survey_data$qk4 == 0)
```

```{r}
rule_9 <- as.numeric(survey_data$qk5 == 102)
```

```{r}
rule_10 <- as.numeric(survey_data$qk5 == 102 & survey_data$qk6 == 1)
```

```{r}
rule_11 <- as.numeric(survey_data$qk7_1 == 1)
```

```{r}
rule_12 <- as.numeric(survey_data$qk7_2 == 1)
```

```{r}
rule_13 <- as.numeric(survey_data$qk7_3 == 1)
```

### Summing up the rules to create the score

```{r}
survey_data$financial_knowledge_score = rowSums(cbind(rule_7, rule_8, rule_9, rule_10, rule_11, rule_12, rule_13))
```

## Financial attitude score

### Recoding some variables 

```{r}
# Specify the columns to be recoded
columns_to_recode <- c("qf10_1", "qf10_2", "qf10_3", "qf10_4", "qf10_5", "qf10_6", "qf10_7", "qf10_8", "qf10_9", "qf10_10", "qf10_11", "qf10_12")

# Recode -97, -98, -99 as 3 in the specified columns
survey_data[columns_to_recode] <- lapply(survey_data[columns_to_recode], function(x) ifelse(x %in% c(-97, -98, -99), 3, x))
```

### Creating the rule

```{r}
# Specify the columns for rescaling
columns_to_rescale <- c("qf10_2", "qf10_8")

# Create a temporary data frame for rescaled values
temp_data <- survey_data

# Rescale values from 1 to 5 to 0 to 4 in the temporary data frame
temp_data[columns_to_rescale] <- temp_data[columns_to_rescale] - 1

# Calculate the average and store it in rule_14
temp_data$rule_14temp <- rowMeans(temp_data[columns_to_rescale], na.rm = TRUE)
rule_14 = temp_data$rule_14temp
```

### Adding the score to the Financial Attitude score to the dataset

```{r}
survey_data$financial_attitude_score = rule_14
```

## Getting the final **Financial literacy score**

```{r}

survey_data$financial_literacy_score <- rowSums(survey_data[, c("financial_behaviour_score", "financial_attitude_score", "financial_knowledge_score")], na.rm = TRUE)

```


# CORRELATION ANALYSIS


## Checking for missing data

```{r}
sum(is.na(survey_data$qd1))
sum(is.na(survey_data$AREA5))
sum(is.na(survey_data$QD5b))
sum(is.na(survey_data$QD7))
sum(is.na(survey_data$QD9))
sum(is.na(survey_data$QD10))
sum(is.na(survey_data$QD12))
```

There are no missing data in the demographic variables

## Creating the correlation matrix

```{r}

# Define the survey design
design <- svydesign(ids = ~1, data = survey_data, weights = ~pesofitc)

# Select relevant variables for analysis
dem_vars <- c("financial_literacy_score", "qd1", "AREA5", "qd5b", "qd7", "qd9", "qd10", "qd12")

# Calculate the survey-weighted correlation matrix
weighted_corr <- svycor(~ financial_literacy_score + qd1 + AREA5 + qd5b + qd7 + qd9 + qd10 + qd12, design)

# Visualize the correlation matrix
corrplot::corrplot(weighted_corr$cors, method = "color")
```

```{r}
# Example for the elbow method
pca_data <- survey_data[, c("financial_literacy_score", "qd1", "AREA5", "qd5b", "qd7", "qd9", "qd10", "qd12")]

# Scale the data for PCA
scaled_data <- scale(pca_data)
wss <- numeric(10)
for (i in 1:10) {
  kmeans_result <- kmeans(scaled_data, centers = i, nstart = 10)
  wss[i] <- kmeans_result$tot.withinss
}
plot(1:10, wss, type = "b", main = "Elbow Method", xlab = "Number of Clusters", ylab = "Within Sum of Squares")
```

```{r}
silhouette_vec <- numeric(10)
for (i in 2:10) {
  kmeans_result <- kmeans(scaled_data, centers = i, nstart = 10)
  cluster_stats <- cluster.stats(dist(scaled_data), kmeans_result$cluster)
  silhouette_vec[i] <- cluster_stats$avg.silwidth
}

plot(2:10, silhouette_vec[-1], type = "b", main = "Silhouette Method", xlab = "Number of Clusters", ylab = "Average Silhouette Width")
```

```{r}
clusters <- kmeans(survey_data[, dem_vars], centers = 5)  # Choose an appropriate number of clusters
survey_data$cluster_label <- as.factor(clusters$cluster)
summary(survey_data$cluster_label)
```

```{r}
# Perform PCA
pca_result <- prcomp(scaled_data, center = TRUE, scale. = TRUE)

# Extract the principal components
pc_scores <- as.data.frame(pca_result$x[, 1:2])

# Combine the PC scores with the cluster labels
pca_data <- cbind(pc_scores, cluster_label = survey_data$cluster_label)

# Scatter plot with different colors for each cluster
ggplot(pca_data, aes(x = PC1, y = PC2, color = factor(cluster_label))) +
  geom_point() +
  labs(title = "PCA Scatter Plot with Clusters",
       x = "Principal Component 1",
       y = "Principal Component 2") +
  theme_minimal()
```

```{r}
# Extract the variable loadings
loadings <- pca_result$rotation[, 1:2]

# Create a dataframe with variable names and loadings for PC1
pc1_loadings <- data.frame(variable = rownames(loadings), loading = loadings[, 1])

# Create a dataframe with variable names and loadings for PC2
pc2_loadings <- data.frame(variable = rownames(loadings), loading = loadings[, 2])

# Order the dataframes by the absolute values of loadings
pc1_loadings <- pc1_loadings[order(abs(pc1_loadings$loading), decreasing = TRUE), ]
pc2_loadings <- pc2_loadings[order(abs(pc2_loadings$loading), decreasing = TRUE), ]

# Visualize the top contributing variables for PC1
ggplot(pc1_loadings, aes(x = reorder(variable, loading), y = loading)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  labs(title = "Top Contributing Variables for PC1",
       x = "Variable",
       y = "Loading") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Visualize the top contributing variables for PC2
ggplot(pc2_loadings, aes(x = reorder(variable, loading), y = loading)) +
  geom_bar(stat = "identity", fill = "lightcoral", color = "black") +
  labs(title = "Top Contributing Variables for PC2",
       x = "Variable",
       y = "Loading") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
## Chage the numerical values indicating the geographic area of Italy into the respective names of the areas.

```{r}
survey_data_temp <- survey_data
survey_data <- survey_data %>%
  mutate(AREA5 = case_when(
    AREA5 == 1 ~ "North-West",
    AREA5 == 2 ~ "North-East",
    AREA5 == 3 ~ "Centre",
    AREA5 == 4 ~ "South",
    AREA5 == 5 ~ "Isles" 
  ))

survey_data <- survey_data %>%
  mutate(qd1 = case_when(
    qd1 == "0" ~ "Female",
    qd1 == "1" ~ "Male"
  ))
```


```{r}
# Change variable names
survey_data <- survey_data %>%
  rename(
    gender = qd1,
    household_members = qd5b,
    age = qd7,
    education = qd9,
    employment_status = qd10,
    birth_country = qd12
  )
```


# EDA

```{r}

#distribution of the population

ggplot(survey_data, aes(x = age)) +
  geom_density(fill = "skyblue", color = "black", alpha = 0.7) +
  geom_vline(aes(xintercept = mean(age), color = "Mean Age"), linetype = "dashed") +
  labs(title = "Density Plot of Age with Mean Highlighted",
       x = "Age",
       y = "Density",
       color = "Legend") +
  scale_color_manual(values = c("red"), labels = c("Mean Age")) +
  theme_minimal()
```


```{r}

#Geographic areas relative frequencies

table(survey_data$AREA5)
prop.table(table(survey_data$AREA5))
```

```{r}
table(survey_data$household_members)
prop.table(table(survey_data$household_members))
```


```{r}
#geographic areas pie-chart

areas <- data.frame(prop.table(table(survey_data$AREA5))*100)

ggplot(areas, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar(theta = "y") +
  ggtitle("Geographical distribution of the participants") +
  geom_text(aes(label = sprintf("%.1f%%", Freq)), position = position_stack(vjust = 0.5)) +
  theme(axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank())
```

```{r}
ggplot(survey_data, aes(x = as.character(education))) + 
  geom_bar(aes(y = ..prop.., group = 1), fill = 'darkorange', width = 0.6) +
  labs(title = " Distribution of Educational qualification",
       x = '',
       y = '%') +
  scale_x_discrete(labels = c("1" = "University-level",
                              "3" = "Complete secondary",
                              "4" = "Some secondary",
                              "5" = "Complete primary",
                              "6" = "Some primary",
                              "7" = "No education"))
```

```{r}
ggplot(survey_data, aes(x = as.character(employment_status))) + 
  geom_bar(aes(y = ..prop.., group = 1), fill = 'darkorange', width = 0.6) +
  labs(title = " Distribution of Employment status",
       x = '',
       y = '%') +
  scale_x_discrete(labels = c("1" = "Self-Employed",
                              "2" = "In paid employment",
                              "4" = "Looking after home",
                              "5" = "Looking for job",
                              "6" = "Retired",
                              "9" = "Student",
                              "10" = "Other"))+
  theme(axis.text.x = element_text(angle = 45, hjust=1))
```

```{r}
sq3sum <- data.frame(value=apply(survey_data[,5:11],2,sum))
sq3sum$key=rownames(sq3sum)
ggplot(data=sq3sum, aes(x=key, y=value, fill=key)) +
geom_bar(colour="white", stat="identity", width= 0.6) +
  labs(title = 'Saving habits',
       x = '',
       y = '')+
  scale_x_discrete(labels = c("qf3_1" = "",
                              "qf3_3" = "",
                              "qf3_4" = "",
                              "qf3_6" = "",
                              "qf3_7" = "",
                              "qf3_8" = "",
                              "qf3_99" = ""))+
  theme(axis.text.x = element_text(angle = 70, hjust=1, size = 7)) +
  scale_fill_discrete(name = 'Habits', labels = c("Saving cash at home or in wallet", 
                                                  "Paying money into a savings account",
                                                  "Giving money to family",
                                                  "Buying financial investment products",
                                                  "Or in some other way",
                                                  "Has not been actively saving",
                                                  "No answer"))
```

```{r}
qf9sum <- data.frame(value=apply(survey_data[,14:24],2,sum))
qf9sum$key=rownames(qf9sum)
ggplot(data=qf9sum, aes(x=key, y=value, fill=key)) +
geom_bar(colour="white", stat="identity", width= 0.6) +
  labs(title = 'Retirement funding plans',
       x = '',
       y = '')+
  scale_x_discrete(labels = c("qf9_1" = "",
                              "qf9_2" = "",
                              "qf9_3" = "",
                              "qf9_4" = "",
                              "qf9_5" = "",
                              "qf9_6" = "",
                              "qf9_7" = "",
                              "qf9_8" = "",
                              "qf9_9" = "",
                              "qf9_10" = "",
                              "qf9_99" = ""))+
  theme(axis.text.x = element_text(angle = 70, hjust=1, size = 7)) +
  scale_fill_discrete(name = 'Habits', labels = c("Drawing a government pension/old-age benefit", 
                                                  "From an occupational or workplace pension plan",
                                                  "From a private pension plan",
                                                  "From selling your financial assets",
                                                  "From selling your non-financial assets",
                                                  "From income generated by your financial or non-financial assets",
                                                  "By relying on a spouse or partner to support you",
                                                  "By relying on your children or other family members to support you",
                                                  "Survivor’s pension",
                                                  "Other",
                                                  "No answer"))
```

```{r}
qprod1csum <- data.frame(value=apply(survey_data[,25:36],2,sum))
qprod1csum$key=rownames(qprod1csum)
ggplot(data=qprod1csum, aes(x=key, y=value, fill=key)) +
geom_bar(colour="white", stat="identity", width= 0.6) +
  labs(title = 'Most bought financial products',
       x = '',
       y = '')+
  scale_x_discrete(labels = c("qprod1c_1" = "",
                              "qprod1c_2" = "",
                              "qprod1c_3" = "",
                              "qprod1c_5" = "",
                              "qprod1c_6" = "",
                              "qprod1c_7" = "",
                              "qprod1c_8" = "",
                              "qprod1c_10" = "",
                              "qprod1c_11" = "",
                              "qprod1c_12" = "",
                              "qprod1c_14" = "",
                              "qprod1c_99" = ""))+
  theme(axis.text.x = element_text(angle = 70, hjust=1, size = 7)) +
  scale_fill_discrete(name = 'Habits', labels = c("Pension or retirement product", 
                                                  "Investment account such as a unit trust",
                                                  "Mortgage or a bank loan secured on a property",
                                                  "unsecured bank loan or a salary/pension-backed
loan",
                                                  "credit card",
                                                  "current/checking account",
                                                  "savings account",
                                                  "Insurance",
                                                  "Stocks and shares",
                                                  "Bonds",
                                                  "A prepaid debit card/ payment card",
                                                  "No answer"))

```


```{r}

# Check if there is a linear relationship between financial literacy score and the demographic covariates

literacy_score_model <- lm(financial_literacy_score ~ gender + as.factor(household_members) + age + as.factor(education) + as.factor(employment_status) + as.factor(birth_country) + AREA5, survey_data[,c(99,100,101,102,103,104,106,107,108,109,110)])
summary(literacy_score_model)

```

```{r}

# Visualize the scores 

literacy_score_model <- lm(formula = financial_literacy_score ~ gender + as.factor(household_members) + 
    age + as.factor(education) + as.factor(employment_status) + 
    as.factor(birth_country) + AREA5, data = survey_data[, c(99, 
    100, 101, 102, 103, 104, 106, 107, 108, 109, 110)])
summary(literacy_score_model)
```

```{r}
plot(survey_data$age,
     literacy_score_model$residuals)
```

```{r}
boxplot(literacy_score_model$residuals ~ survey_data$gender, main = "Residuals by gender")
boxplot(literacy_score_model$residuals ~ as.factor(survey_data$household_members), main = "Residuals by household members")
boxplot(literacy_score_model$residuals ~ as.factor(survey_data$education), main = "Residuals by education")
boxplot(literacy_score_model$residuals ~ as.factor(survey_data$employment_status), main = "Residuals by empolyment status")
# A linear model is not able to predict financial literacy score.
```

# Divisione in classi

```{r}
dem_data = survey_data_temp[, dem_vars]
dem_data <- dem_data %>%
  rename(
    gender = qd1,
    household_members = qd5b,
    age = qd7,
    education = qd9,
    employment_status = qd10,
    birth_country = qd12,
    area = AREA5)
```

```{r}
dem_data <- dem_data %>%
  mutate(gender = case_when(
    gender == "0" ~ "Female",
    gender == "1" ~ "Male"
  ))
```

```{r}
dem_data <- dem_data %>%
  mutate(area = case_when(
    area == 1 ~ "North",
    area == 2 ~ "North",
    area == 3 ~ "Centre",
    area == 4 ~ "South",
    area == 5 ~ "Isles" 
  ))
```


```{r}
dem_data <- dem_data %>%
  mutate(household_members = case_when(
    household_members == 1 ~ "Little to Medium",
    household_members == 2 ~ "Little to Medium",
    household_members == 3 ~ "Little to Medium",
    household_members == 4 ~ "Little to Medium",
    household_members == 5 ~ "Big",
    household_members == 6 ~ "Big"
  ))
```

```{r}
# Define breaks for categorization
age_breaks <- c(18, 34, 60, Inf)

# Apply cut function to create age categories
dem_data$age <- cut(dem_data$age, breaks = age_breaks, labels = c("18-34", "35-60", "61+"), include.lowest = TRUE)
```

```{r}
dem_data <- dem_data %>%
  mutate(education = case_when(
    education == 1 ~ "University level Education",
    education == 3 ~ "Average Education",
    education == 4 ~ "Average Education",
    education == 5 ~ "Low Education",
    education == 6 ~ "Low Education",
    education == 7 ~ "Low Education"
  ))
```

```{r}
dem_data <- dem_data %>%
  mutate(birth_country = case_when(
    birth_country == "0" ~ "Other",
    birth_country == "1" ~ "Italy"
  ))
```

```{r}
dem_data <- dem_data %>%
  mutate(employment_status = case_when(
    employment_status == 1 ~ "Self Employed",
    employment_status == 2 ~ "In paid employement",
    employment_status == 4 ~ "Looking after the home",
    employment_status == 5 ~ "Looking for work",
    employment_status == 6 ~ "Retired",
    employment_status == 9 ~ "Student",
    employment_status == 10 ~ "Other"
  ))
```

```{r}
# Define breaks for financial literacy score categories
score_breaks <- c(0, 7.9, 13.9, Inf)

# Apply cut function to create score categories
dem_data$financial_literacy_score_classes <- cut(dem_data$financial_literacy_score, breaks = score_breaks, labels = c("Low Financial Score", "Medium Financial Score", "High Financial Score"), include.lowest = TRUE)
```


# ANOVA E PCA

```{r}
#MODELLI CON WEIGHTS

# Esegui un'ANOVA 
modello_anova <- aov(financial_literacy_score ~ education, data = dem_data, weights = survey_data$pesofitc)
summary(modello_anova)

# Esegui un'ANOVA
modello_anova2 <- aov(financial_literacy_score ~ gender, data = dem_data, weights = survey_data$pesofitc)
summary(modello_anova2)

# Esegui un'ANOVA
modello_anova3 <- aov(financial_literacy_score ~ area, data = dem_data, weights = survey_data$pesofitc)
summary(modello_anova3)

# Esegui un'ANOVA
modello_anova4 <- aov(financial_literacy_score ~ household_members, data = dem_data, weights = survey_data$pesofitc)
summary(modello_anova4)

# Esegui un'ANOVA
modello_anova5 <- aov(financial_literacy_score ~ age, data = dem_data, weights = survey_data$pesofitc)
summary(modello_anova5)

# Esegui un'ANOVA
modello_anova6 <- aov(financial_literacy_score ~ employment_status, data = dem_data, weights = survey_data$pesofitc)
summary(modello_anova6)

# Esegui un'ANOVA
modello_anova7 <- aov(financial_literacy_score ~ birth_country, data = dem_data, weights = survey_data$pesofitc)
summary(modello_anova7)
```


```{r}

# Esempio di dati PCA
dati_pca <- survey_data_temp[, c('financial_literacy_score', 'qd1', 'AREA5', 'qd5b', 'qd7', 'qd9', 'qd10', 'qd12')]

# Esegui l'analisi delle componenti principali (PCA)
pca_result <- prcomp(dati_pca, scale. = TRUE, weights = survey_data$pesofitc)

# Estrai i risultati della PCA
scores <- as.data.frame(pca_result$x)

# Crea un DataFrame con i punteggi e aggiungi una colonna per l'etichetta dell'osservazione
df_pca <- cbind(scores, osservazione = rownames(scores))

# In this graph we can see that the first two dimensions explain more or less the 37% of variance.
fviz_eig(pca_result,addlabels = TRUE)

# We have the contributions of the variables to the two dimensions: in the first one, the variables qd7, qd5b and qd9 have a contributions of more than 10%, while in the second one the variables with high contributions are financial literacy score, AREA5, qd10 and qd9.

fviz_contrib(pca_result, choice = "var", axes = 1)
fviz_contrib(pca_result, choice = "var", axes = 2)

# The same explanation for the previous graphs can be see here.
fviz_pca_var(pca_result, col.var="contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)

# The same explanation for the previous graphs can be see here the dots are the individuals mapped on bidimensional space of PCA, while cos2represents the quality of their mapping expressed through a gradient of colors. If they are more blue, more their mapping is good. Among the previous graph, we have the adding of individuals, while the lines are equal. 
fviz_pca_biplot(pca_result,geom.ind ='point',col.ind = 'cos2',repel = TRUE,palette = 'jco',gradient.cols = "RdYlBu")
```
